\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1.8cm, right=1.8cm, top=1.8cm, bottom=1.8cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5} % For icons
\usepackage{enumitem} % For custom itemize styles
\usepackage{ragged2e} % For better text justification
\usepackage{amsmath} % For \text command

% Define custom colors - Using a safe professional color (Steel Blue)
\definecolor{maincolor}{HTML}{4682B4}      % Steel Blue
\definecolor{maincolorlight}{HTML}{ADD8E6}  % Light Steel Blue
\definecolor{venuecolor}{HTML}{005f89}   % Dark Steel Blue for venues
\definecolor{emphasis}{HTML}{222222}
\definecolor{body}{HTML}{333333}
\definecolor{linkcolor}{HTML}{003366}     % An even darker shade of blue for links

% Hyperlink formatting
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    citecolor=linkcolor % Optional: Color for citation links if you were using biblatex
}

\setlength{\parindent}{0pt}

% Custom section heading command with centered rules
\newcommand{\cvsection}[1]{%
    \vspace{10pt}
    \noindent\hfill\kern0.5em
    {\Huge \textbf{\textcolor{maincolor}{#1}}}%  Made section heading larger
    \kern0.5em\hfill\vspace{8pt}
}

\begin{document}
\RaggedRight % To prevent hyphenation and improve visual flow

% Name and Contact Info
\begin{center}
    {\Huge \textbf{\MakeUppercase{Rasa Hosseinzadeh}}} \\[5pt]
    \href{mailto:rasa.hosseinzadeh@gmail.com}{\textcolor{maincolor}{\faEnvelope}\hspace{0.5em} Email} \hspace{1.5em}
    \href{https://github.com/rasaHosseinzadeh}{\textcolor{maincolor}{\faGithub}\hspace{0.5em} GitHub} \hspace{1.5em}
    \href{https://linkedin.com/in/rasa-hosseinzadeh-6204a6208}{\textcolor{maincolor}{\faLinkedin}\hspace{0.5em} LinkedIn} \hspace{1.5em}
    \href{https://scholar.google.com/citations?user=1Evd7mYAAAAJ}{\textcolor{maincolor}{\faGraduationCap}\hspace{0.5em} Scholar}
\end{center}
\vspace{15pt}

% Education Section
\cvsection{Education}

{\Large \textbf{\textcolor{maincolor}{University of Toronto}}} \\
\textbf{M.Sc.} \hspace{1.4em} Computer Science \hspace{18.0em} GPA: 4/4 \hfill 2019 -- 2020 \\
\vspace{8pt}

{\Large \textbf{\textcolor{maincolor}{Sharif University of Technology}}} \\
\textbf{B.Sc.} \hspace{1.7em} Double Major in Software Engineering and Mathematics \hfill GPA: 19.04/20 \hfill 2013 -- 2018 \\
\vspace{15pt}

% Experience Section
\cvsection{Experience}


{\Large \textbf{\textcolor{maincolor}{Layer 6}}} \\
\textbf{Senior Research Machine Learning Scientist} \hfill 2025 -- Present \\
\textbf{Machine Learning Scientist} \hfill 2021 -- 2025
\begin{itemize}[noitemsep, topsep=4pt, leftmargin=1.5em, label=\textcolor{maincolorlight}{$\circ$}]
    \item Developed in-context learning strategies for tabular foundation models.
    \item Investigated the manifold hypothesis in the context of generative models.
    \item Implemented automated adjudication systems for life insurance claims.
    \item Evaluated and compared various evaluation metrics for generative models.
    \item Conducted research on non-autoregressive transformer models for translation.
\end{itemize}
\vspace{10pt}

{\Large \textbf{\textcolor{maincolor}{Vector Institute}}} \\
\textbf{Research Assistant} \hfill 2019 -- 2021
\begin{itemize}[noitemsep, topsep=4pt, leftmargin=1.5em, label=\textcolor{maincolorlight}{$\circ$}]
    \item Established theoretical convergence rates for ULA in non-convex and non-smooth settings.
\end{itemize}
\vspace{15pt}

% Publications Section
\cvsection{Publications}
\begin{itemize}[noitemsep, topsep=4pt, leftmargin=0em, label=\textcolor{maincolorlight}{$\circ$}]
    \item A Geometric Framework for Understanding Memorization in Generative Models. {\textcolor{venuecolor}{\href{https://arxiv.org/abs/2411.00113}{\textit{arXiv Preprint}}}}.
    \item TabDPT: Scaling Tabular Foundation Models. {\textcolor{venuecolor}{\href{https://arxiv.org/abs/2410.18164}{\textit{arXiv Preprint}}}}.
    \item Inconsistencies in Consistency Models: Better ODE Solving Does Not Imply Better Samples. {\textcolor{venuecolor}{\href{https://openreview.net/forum?id=2p4ES8QPUi}{NeurIPS 2024 Workshop}}}.
    \item MSC-SQL: Multi-Sample Critiquing Small Language Models for Text-to-SQL Translation. {\textcolor{venuecolor}{\href{https://openreview.net/forum?id=RubZlwPv6D}{NeurIPS 2024 Workshop}}}.
    \item Retrieval \& Fine-Tuning for In-Context Tabular Models. {\textcolor{venuecolor}{\href{https://arxiv.org/abs/2406.05207}{NeurIPS 2024}}}.
    \item A Geometric View of Data Complexity: Efficient Local Intrinsic Dimension Estimation with Diffusion Models. {\textcolor{venuecolor}{\href{https://arxiv.org/abs/2406.03537}{NeurIPS 2024 \textbf{(Spotlight)}}}}.
    \item Deep Generative Models through the Lens of the Manifold Hypothesis. {\textcolor{venuecolor}{\href{https://openreview.net/forum?id=a90WpmSi0I}{TMLR 2024}}}.
    \item Exposing Flaws of Generative Model Evaluation Metrics and Their Unfair Treatment of Diffusion Models. {\textcolor{venuecolor}{\href{https://papers.nips.cc/paper_files/paper/2023/hash/0bc795afae289ed465a65a3b4b1f4eb7-Abstract-Conference.html}{NeurIPS 2023}}}.
    \item DiMS: Distilling Multiple Steps of Iterative Non-Autoregressive Transformers for Machine Translation. {\textcolor{venuecolor}{\href{https://aclanthology.org/2023.findings-acl.542}{Findings of ACL 2023}}}.
    \item Convergence of Langevin Monte Carlo in Chi-squared and R\'enyi Divergence. {\textcolor{venuecolor}{\href{https://proceedings.mlr.press/v151/erdogdu22a.html}{AISTATS 2022}}}.
    \item On the Convergence of Langevin Monte Carlo: The Interplay Between Tail Growth and Smoothness. {\textcolor{venuecolor}{\href{https://proceedings.mlr.press/v134/erdogdu21a.html}{COLT 2021}}}.
\end{itemize}

\end{document}
